Red States = Red Flags?

### 2024-02-15 paper/paper.qmd
changes to paper

# Merge with states map data
map_data_merged <-
  left_join(states_map, data_merged, by = c("region" = "stname"))
```

```{r echo=FALSE, message=FALSE}
# Plot
ggplot(map_data_merged) +
  geom_polygon(
    aes(
      x = long,
      y = lat,
      group = group,
      fill = `Fraction of State Senate that is Democrat`
    ),
    color = "white"
  ) +
  geom_text(
    data = map_data_merged %>% group_by(region) %>% summarise(
      long = mean(long),
      lat = mean(lat),
      numbirths = first(births)
    ),
    aes(x = long, y = lat, label = numbirths),
    size = 3,
    check_overlap = TRUE
  ) +
  scale_fill_gradient(low = "red",
                      high = "blue",
                      name = "Democrat Fraction") +
  coord_fixed(1.3) +
  labs(title = "2019 Births and Democrat Fraction in State Senate by State") +
  theme_void() +
  theme(legend.position = "right")
```

>>>>

# Merge with states map data
map_data_merged <-
  left_join(states_map, data_merged, by = c("region" = "stname"))

# Plot
ggplot(map_data_merged) +
  geom_polygon(
    aes(
      x = long,
      y = lat,
      group = group,
      fill = `Fraction of State Senate that is Democrat`
    ),
    color = "white"
  ) +
  geom_text(
    data = map_data_merged %>% group_by(region) %>% summarise(
      long = mean(long),
      lat = mean(lat),
      numbirths = first(numbirth1544)
    ),
    aes(x = long, y = lat, label = numbirths),
    size = 3,
    check_overlap = TRUE
  ) +
  scale_fill_gradient(low = "red",
                      high = "blue",
                      name = "Democrat Fraction") +
  coord_fixed(1.3) +
  labs(title = "2019 Births and Democrat Fraction in State Senate by State") +
  theme_void() +
  theme(legend.position = "right")
```
